Untitled

### 2024-11-08 code/manuscript_altanalysis.Rmd
estimate of change

df.temptemp %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
  filter(!is.na(value) & value_min > 1) %>% 
  group_by(Post, Treat) %>% 
  select(Closed) %>% 
  summarise_all(mean.nas)

>>>>

df.temptemp %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
  filter(!is.na(value) & value_min > 1) %>% 
  group_by(Post, Treat) %>% 
  select(Closed) %>% 
  summarise(mean.nas, n())

df.temptemp %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
  filter(!is.na(value) & value_min > 1) %>% 
  group_by(Post, Treat) %>% 
  select(Closed) %>% 
  summarise(n())

df.temptemp %>% 
  filter(Tx == 1 & Closed == 100 & value > 2)
